Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-04-26 area_agg_seq_tsas.tex
improved according to Jan's comment

Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal 
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that our inputs are only
subdivisions~$\Pstart$ and~$\Pgoal$.
We generate a subdivision (node) only when we want to visit it.

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
%\parencite[e.g.,][\sect25.2]{Cormen2009},
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.

>>>>

Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal 
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that our inputs are only
subdivisions~$\Pstart$ and~$\Pgoal$
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
We generate a subdivision (node) only when we want to visit it.

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
%\parencite[e.g.,][\sect25.2]{Cormen2009},
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The \Astar algorithm can be seen as 
a refinement of Dijkstra's algorithm, 
which for a user-specified given source 
computes shortest paths to all other nodes in an edge-weighted graph
\parencite{Dijkstra1959}. 
Even when using Dijkstra's algorithm 
to compute only a single shortest path to a user-specified destination, 
a large number of nodes need to be explored. 
The same holds for shortest-path algorithms 
that make use of a topological order of the nodes 
in a directed acyclic graph. 
Compared to these algorithms, 
the \Astar algorithm can greatly reduce the number of explored nodes.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.
